### 2021-02-09 paper/model_validation.tex
Release v2.0.0.
Update text to model validation.

\subsection{In-Sample Fit}

Despite fitting only four free parameters, the in-sample fit is very good. The best fit
is achieved in the largest age groups. This is so mechanically, because we weight the
deviations between simulated and observed infection rates by group sizes. The worst fit
is achieved for the 80 to 100 years old. The model predicts too few infections for these
groups because they have very few contacts in all contact types we have included so far.
We plan to address this issue soon by adding another contact type that captures all
contacts in the data by \citet{Mossong2008} that we have not included so far. Moreover,
we expect an improved model fit when we allow for more free parameters.

\begin{figure}[!tp]
    \centering
    \includegraphics[width=\textwidth]{../figures/goodness_of_fit_by_age_group}
    \caption{Reported vs. simulated weekly incidence rates of infections.}
    \label{fig:goodness_of_fit}
    \figurenotes{
        The figure shows the weekly incidence rates per 100,000 people for the reported
        (red line) versus the simulated infections rates (blue line) for age groups
        available in the data provided by the Robert-Koch Institut.
    }
\end{figure}

\subsection{Out-of-Sample Fit}

We can assess the out-of-sample fit by projecting the effect of the lockdown light and
comparing it to case numbers until now. It is important to note that this is not just a
simple extrapolation of a time trend because the lockdown light only started after the
estimation period. The out-of-sample fit can be assessed in
Figure~\ref{fig:out-of-sample-fit}.

@@

The model correctly predicts the effect of the lockdown light with reasonable accuracy.
In particular, the actual case numbers are between our neutral and pessimistic
projection. The plot also shows that ending the lockdown light as planned on November 30
would lead to an explosive growth in case numbers in all scenarios.

>>>>

\subsection{In-Sample Fit}
\label{sub:in_sample_fit}

Despite fitting only four infection probabilities, the in-sample fit is very good.
The best fit is achieved in the largest age groups.
This is so mechanically, because we weigh the
deviations between simulated and observed infection rates by group sizes. The worst fit
is achieved for the 80 to 100 years old.
There are three reasons for this: Firstly, we only model private households at
the moment, meaning that nursing homes are not part of the synthetic population we
simulate. Since community housing residents are part of the German Mikrozensus
\citep{FDSAeDBUDL2018} which forms the basis for our synthetic population, we can and
plan to include community housing residents in the near future.
Secondly, the elderly, especially nursing home residents, are tested more often than
the general population leading to more cases being detected in this age group.
We are currently working to include age-variant testing strategies,
using \href{https://ars.rki.de/Content/COVID19/Main.aspx}{data by the RKI}
\citep{Seifried2020}.

\begin{figure}[h]
    \centering
    \includegraphics[width=1.1\textwidth]{../figures/goodness_of_fit_by_age_group}
    \caption{Reported vs. simulated weekly incidence rates of infections.}
    \label{fig:goodness_of_fit}
    \figurenotes{
        The figure shows the weekly incidence rates per 100,000 people for the reported
        (red line) versus the simulated infections rates (blue line) for age groups
        available in the data provided by the Robert-Koch Institut.
    }
\end{figure}

\FloatBarrier

\subsection{Out-of-Sample Fit}
\label{sub:out_of_sample_fit}

We can assess the out-of-sample fit by projecting the effect of the lockdown light and
comparing it to case numbers until mid of November. It is important to note that this
is not just a simple extrapolation of a time trend because the lockdown light only started
after the estimation period. The out-of-sample fit can be assessed in
Figure~\ref{fig:out-of-sample-fit}.

@@

The model correctly predicts the effect of the lockdown light with reasonable accuracy.
In particular, the actual case numbers are between our neutral and pessimistic
projection. The plot also shows that ending the lockdown light on November 30, as was
originally planned, would lead to an explosive growth in case numbers in all scenarios.
